Fast and robust ancestry inference using principal component analysis

### 2018-06-22 doc/paper/paper.tex
Edit author list

\title{
  Fast and robust ancestry inference
  using principal component analysis
}
\author{Daiwei Zhang, Rounak Dey, Seunggeun Lee}
\date{}

\begin{document}

\maketitle

\begin{abstract}

 Population stratification (PS) is a major confounder in genome-wide association studies (GWAS) and can lead to false positive associations. To adjust for PS, principal component analysis (PCA)-based ancestry prediction has been widely used. This approach first performs PCA on the reference samples with detailed ancestry information and then uses the reference sample PCA results to predict the PC scores of the study samples. Simple Projection (SP) and Augmentation-Decomposition-Transformation (ADP), such as LASER and TRACE, are popular methods for predicting PC scores. However, they are either biased or computationally expensive. For example, the predicted PC scores from SP can be biased toward NULL. On the other hand, since ADP requires running PCA separately for each study sample on the augmented data set, its computational cost is high.

>>>>

\title{
  Fast and robust ancestry inference
  using principal component analysis
}
\author{Daiwei Zhang, Rounak Dey, Sehee Kim, Seunggeun Lee}
\date{}

\begin{document}
\maketitle

\begin{abstract}
Population stratification (PS) is a major confounder in genome-wide association studies (GWAS) and can lead to false positive associations. To adjust for PS, principal component analysis (PCA)-based ancestry prediction has been widely used. This approach first performs PCA on the reference samples with detailed ancestry information and then uses the reference sample PCA results to predict the PC scores of the study samples. Simple Projection (SP) and Augmentation-Decomposition-Transformation (ADP), such as LASER and TRACE, are popular methods for predicting PC scores. However, they are either biased or computationally expensive. For example, the predicted PC scores from SP can be biased toward NULL. On the other hand, since ADP requires running PCA separately for each study sample on the augmented data set, its computational cost is high.
